% This file uses the resume document class (res.cls)
\documentclass{res}
\usepackage{textcomp}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\begin{document}

\name{KYRYLO SILIN\\[12pt]} % the \\[12pt] adds a blank
\address{Kharkiv, Ukraine\\silin@kyrylo.org\\+380 98 909-30-34}

\begin{resume}

  \section{JOB OBJECTIVE}
  Senior software engineer with a master’s in computer science and vast
  experience in web development and remote work. Open-source contributor and
  maintainer of popular projects (Pry, used by 35\% of Ruby developers; Airbrake
  Ruby, over 20 million downloads). Seeking to leverage leadership to become
  your company’s next senior software engineer and continue to grow and learn
  from others.

  \section{EDUCATION}
  Kharkiv National University of Radioelectronics, Kharkiv, Ukraine \\
  Master of Science, Computer Science \hfill January 2015 \\
  Major in Information Control Systems and Technology \\

  Kharkiv National University of Radioelectronics, Kharkiv, Ukraine \\
  Bachelor of Science, Computer Science \hfill August 2012 \\
  Major in Information Control Systems and Technology \\

  \section{EXPERIENCE}
  \vspace{-0.1in}

  \begin{tabbing}
    \hspace{2.3in}\= \hspace{2.6in}\= \kill
    {\bf Software Engineer}  \>Airbrake (owned by LogicMonitor) \>
    \hspace{-0.2in} Apr 2021 - Jan 2023\\
    \>Santa Barbara, CA, United States
  \end{tabbing}\vspace{-20pt}
  Added support for notifier configs, which helped Airbrake customers alter
  their notifiers' behavior at runtime. Launched new functionality like Teams
  and the Audit Log. Assisted with the development of spike detection in
  customer error and APM usage to apply automatic discounts. I have worked on
  the billing system relaunch. In doing so, I changed how the old code
  communicates with the Stripe API. I also used Swagger to define and implement
  internal APIs and deploy microservices to the Kubernetes cluster.

  \begin{tabbing}
    \hspace{2.3in}\= \hspace{2.6in}\= \kill
    {\bf Software Engineer}  \>Airbrake \> \hspace{-0.3in} July 2015 - April 2021\\
    \>San Francisco, CA, United States
  \end{tabbing}\vspace{-20pt}
  Redesigned and reimplemented the open-source Airbrake notifier library for the
  Ruby programming language from scratch. Added performance monitoring
  capabilities and improved existing APIs for other notifier libraries written
  in other programming languages. Developed the dashboard using Angular and
  TypeScript. I have been involved in developing the Application Performance
  Monitoring feature from the start. Developed and maintained a mature Ruby on
  Rails application. Developed the HTTP backend using the Go and Ruby
  programming languages. Wrote documentation for existing notifier APIs, the
  Airbrake HTTP API, application documentation, and more.


  \begin{tabbing}
    \hspace{2.3in}\= \hspace{2.6in}\= \kill
    {\bf Software Engineer (internship)}  \>Bugsnag \> \hspace{-0.2in} July-September  2014\\
    \>San Francisco, CA, United States
  \end{tabbing}\vspace{-20pt}
  Worked on the front-end part of the OnAir Player (a distributed music player)
  written in JavaScript. Been fixing bugs related to the responsiveness of the
  application for web users. Created a demo application for the iPad using
  Sencha Touch (front-end, JavaScript) and Salesforce (the Apex programming
  language) to help other developers understand how to integrate applications
  with the Salesforce ecosystem.

  \begin{tabbing}
    \hspace{2.3in}\= \hspace{2.6in}\= \kill
    {\bf Software Engineer}  \>Entenso Ltd \> \hspace{-0.2in} June-November 2013\\
    \>Kharkiv, Ukraine
  \end{tabbing}\vspace{-20pt}
  Worked on the front-end part of the OnAir Player (a distributed music player)
  written in JavaScript. Been fixing bugs related to the responsiveness of the
  application for web users. Created a demo application for the iPad using
  Sencha Touch (front-end, JavaScript) and Salesforce (the Apex programming
  language) to help other developers understand how to integrate applications
  with the Salesforce ecosystem.

  \begin{tabbing}
    \hspace{2.3in}\= \hspace{2.6in}\= \kill
    {\bf Web Developer} \> Freelance \> \hspace{-0.5in} April 2010 - August 2013 \\
  \end{tabbing}\vspace{-20pt}
  Worked with different clients on a freelance basis. Some of my clients:
  Primate Inc (a platform that shortlists job candidates for interviews based on
  what they can do), DJ TechTools (the world's leading web community dedicated
  to digital DJing).

  \section{PUBLICATIONS}
  ``How I interned at a startup in San Francisco and flew home'' (in Russian)
  \href{https://habr.com/post/285666/}{https://habr.com/post/285666/},
  September 2014.

  ``So what is ‘binding.pry’ exactly?''
  \href{http://kyrylo.org/2013/05/30/so-what-is-binding-pry-exactly}
  {http://kyrylo.org/2013/05/30/so-what-is-binding-pry-exactly},
  May 2013

  \section{PERSONAL PROJECTS}

  \href{https://github.com/kyrylo/rmarshal}{rmarshal}
  \\
  An Erlang library for deserialising Ruby objects dumped by Marshal.dump into
  Erlang terms.

  \href{https://github.com/kyrylo/fast_method_source}{fast\_method\_source}
  \\
  A Ruby C extension for querying methods, procs and lambdas for their source
  code and comments. Extremely fast.

  \href{https://github.com/kyrylo/netstring}{netstring}
  \\
  A Go library for packing and parsing netstrings, self-delimiting encoding of
  strings.

  \href{https://github.com/kyrylo/system_browser_client}{system\_browser\_client}
  \\
  A desktop app for browsing Ruby code. Just click to get details about a module
  or class and explore its namespace or see the source of a method. Uses System
  Navigation, another library of mine that provides navigation and introspection
  capabilities for Ruby programs.

  \section{OPEN SOURCE CONTRIBUTIONS}

  \href{https://github.com/airbrake/airbrake-ruby/commits?author=kyrylo}{Airbrake
    Ruby commits}
  \\
  I have redesigned the Airbrake library for Ruby from scratch and maintained
  it for 7+ years.

  \href{https://github.com/pry/pry/commits?author=kyrylo}{Pry commits}
  \\
  I am a core team member of the Pry REPL project for the Ruby
  programming language.

  \section{COMPUTER SKILLS}

  Proficient programming skills in Ruby, JavaScript \& Go. Familiarity with
  different programming paradigms (OOP, functional, procedural, etc.) and
  experience with various programming languages (mostly for hobbies). Experience
  with Kubernetes and AWS.

  \section{HOBBIES}

  Learning new programming languages, learning new natural languages, making
  open source contributions, hiking in the mountains, cycling, history,
  trying new foods.

\end{resume}
\end{document}
